Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
new stuff

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "distinction.new.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "make.broker.cliques.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r Toy Networks Plots}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
```

```{r Toy Network Distinction Tables}
    tab.cent(distinction(g1), name = "star", label = "tab:star")
    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
    tab.cent(distinction(g5), name = "circle", label = "tab:circle")
    tab.cent(distinction(g6), name = "circleplus", label = "tab:circleplus")
    tab.cent(distinction(g6), name = "kite", label = "tab:kite")
```

@@

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   set.seed(12345)
   b <- connect.caves(c = 4, nc = 4, n = 20)
```

```{r}
   source(here("Functions", "distinction.new.R"))
   distinction(g1)
   distinction.new(g1, norm = TRUE)
```

```{r}
   c <- lapply(b, distinction.new, norm = FALSE)
```

```{r}
   gg2 <- function(x, lay.o = "kk") {
      n <- vcount(x)
      V(x)$name <- 1:n
      c <- c(rep("tan2", n))
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) 
      #ylim(-4, 3.5) + xlim(-4, 3.25) 
      return(w)
      }
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1, 6, 11, 16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples.png"), width = 10, height = 10, units = "in")
```

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "make.broker.cliques.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r Toy Networks Plots}
   png(here("Plots", "Toys", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
```

```{r Toy Network Distinction Tables}
    tab.cent(distinction(g1), name = "star", label = "tab:star")
    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
    tab.cent(distinction(g5), name = "circle", label = "tab:circle")
    tab.cent(distinction(g6), name = "circletriangle", label = "tab:circletriangle")
    tab.cent(distinction(g7), name = "circlelong", label = "tab:circlelong")
    tab.cent(distinction(g8), name = "clique", label = "tab:clique")
    tab.cent(distinction(g9), name = "kite", label = "tab:kite")
    tab.cent(distinction(g10), name = "wheel", label = "tab:wheel")
```

@@

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   set.seed(456)
   b <- connect.caves(c = 4, nc = 4, n = 24)
   gg2 <- function(x, lay.o = "kk") {
      n <- vcount(x)
      V(x)$name <- 1:n
      d <- distinction(x)[, 3]
      c <-  vector(mode = "character", length = length(d))
      c[which(d < -0.05)] <- "tan2"
      c[which(d > 0.05)] <- "blue"
      c[which(d >=-0.05 & d <= 0.05)] <- "purple"
      c[which(d == max(d))] <- "red"
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) 
      return(w)
      }
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:4)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples1.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(5:8)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples2.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(9:12)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples3.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(13:16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples4.png"), width = 10, height = 10, units = "in")
```
